Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-29 paper/abstract.tex
Updated and rearranged

We introduce hierarchically supervised latent Dirchlet allocation (HSLDA), a model for hierarchically and multiply-labeled bag-of-words data.  Out-of-sample label prediction is the primary goal of this work; however, improved dimensionality reduction is also of interest.  We define a model that uses probit regressors on a conditionally dependent label hierarchy tied to latent Dirichlet allocation (LDA).  We find that the additional signal that comes from multiple, hierarchically constrained labels substantially improves out-of-sample label prediction in comparison to supervised LDA approaches that don't utilize information derived from the structure of the label space.   We demonstrate HSLDA on large-scale data from medical document labeling and retail product categorization tasks and show both improved label prediction performance and show evidence that the learned topic model improves as a result of using this signal too.

>>>>

We introduce hierarchically supervised latent Dirchlet allocation (HSLDA), a model for hierarchically and multiply-labeled bag-of-words data.  Out-of-sample label prediction is the primary goal of this work; however, improved dimensionality reduction is also of interest.  We define a model that uses probit regressors on a conditionally dependent label hierarchy tied to latent Dirichlet allocation (LDA).  We find that the additional signal that comes from multiple, hierarchically constrained labels substantially improves out-of-sample label prediction in comparison to supervised LDA approaches that don't utilize information derived from the structure of the label space.   We demonstrate HSLDA on large-scale data from medical document labeling and retail product categorization tasks.  We show improved label prediction performance and evidence that the learned topic model also improves as a result of using this signal.

### 2011-05-29 paper/introduction.tex
Updated and rearranged

There exist many sources of unstructured data that have been partially or completely categorized by human editors.  In this paper we focus on unstructured textual data that has been, at least in part, manually categorized.  Examples include but are not limited to webpages and curated hierarchical directories of the same \citep{DMOZ}, product descriptions and catalogs (e.g.~\citep{AMAZON} as available from \citep{SNAP}), and patient hospital treatment transcripts and  codes applied to them for bookkeeping and insurance purposes (e.g.~hospital discharge records with International Classification of Disease 9th Revision,
Clinical Modification (ICD-9-CM) codes assigned \cite{}).  In this work we show how to combine these two sources of information using a single model that allows one to automatically categorize new text documents, suggest labels that might be inaccurate, compute improved similarities between documents for information retrieval purposes, and more.  The models and techniques that we develop in this paper are applicable in other domains as well, namely, any unstructured representations of data that have been hierarchically classified (e.g.~image catalogs with bag-of-feature image representations).

In this work we extend supervised latent Dirichlet allocation (sLDA) \cite{BleiMcAuliffe2008} to take advantage of hierarchical supervision.  sLDA is latent Dirichlet allocation (LDA) \cite{Blei2003} augmented with per document ``supervision;''  often taking the form of a single numerical or categorical ``label.''  More generally this ``supervision'' can be seen as extra data  about a document;  for instance its quality or relevance (e.g.~online review scores), marks given to written work (e.g.~essay grades), or the number of times a web page is linked.  These labels are usually generatively modeled as having been conditional draw given an inferred document-specific topic mixture.  It has been demonstrated that the signal provided by this supervision can result in better, task-specific document models and can also lead to good label prediction for out-of-sample data \cite{}.

@@

The remainder of this paper is structured as follows.  In Section~\ref{sec:methods} we introduce hierarchically supervised LDA (HSLDA), in Section~\ref{sec:related_work} we review related work, and in Section~\ref{sec:experiments} we apply HSLDA to health care and web retail data, showing predictive performance and improved topic generation.

>>>>

There exist many sources of unstructured data that have been partially or completely categorized by human editors.  In this paper we focus on unstructured textual data that has been, at least in part, manually categorized.  Examples include but are not limited to webpages and curated hierarchical directories of the same \citep{DMOZ}, product descriptions and catalogs (e.g.~\citep{AMAZON} as available from \citep{SNAP}), and patient hospital treatment transcripts and  codes applied to them for bookkeeping and insurance purposes (e.g.~hospital discharge records with International Classification of Disease 9th Revision,
Clinical Modification (ICD-9-CM) codes assigned \cite{ICD9}).  In this work we show how to combine these two sources of information using a single model that allows one to automatically categorize new text documents, suggest labels that might be inaccurate, compute improved similarities between documents for information retrieval purposes, and more.  The models and techniques that we develop in this paper are applicable in other domains as well, namely, any unstructured representations of data that have been hierarchically classified (e.g.~image catalogs with bag-of-feature image representations).

In this work we extend supervised latent Dirichlet allocation (sLDA) \cite{BleiMcAuliffe2008} to take advantage of hierarchical supervision.  sLDA is latent Dirichlet allocation (LDA) \cite{Blei2003} augmented with per document ``supervision'';  often taking the form of a single numerical or categorical ``label.''  More generally this ``supervision'' can be seen as extra data  about a document;  for instance its quality or relevance (e.g.~online review scores), marks given to written work (e.g.~essay grades), or the number of times a web page is linked.  These labels are usually generatively modeled as having been conditionally draw given an inferred document-specific topic mixture.  It has been demonstrated that the signal provided by this supervision can result in better, task-specific document models and can also lead to good label prediction for out-of-sample data \cite{BleiMcAuliffe2008}.

@@

The remainder of this paper is structured as follows.  In Section~\ref{sec:related_work} we review related work, in Section~\ref{sec:model} we introduce hierarchically supervised LDA (HSLDA), and in Section~\ref{sec:experiments} we apply HSLDA to health care and web retail data, showing predictive performance and improved topic generation.
